---
title: "Getting started with igfetchr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with igfetchr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Introduction

igfetchr is a small, beginner-friendly wrapper around the IG Trading REST API (labs.ig.com). It provides functions to authenticate and fetch market search results, current prices, historical prices, and account summaries — returning tidy tibbles.

**Disclaimer:** Trading CFDs and spread bets carry a high risk of losing money. This vignette demonstrates data access only; igfetchr is not financial advice.

# Offline / testing mode

To make examples and tests deterministic and CRAN-friendly, igfetchr supports an offline testing mode. Set the environment variable `IGFETCHR_TESTING = "true"` and the package will return mock tokens and accept `mock_response` data frames for endpoints.

```{r testing-mode}
Sys.setenv(IGFETCHR_TESTING = "true")
library(igfetchr)
```

# Authenticate (mock)

This example uses the package's testing mode and returns a mock auth list instantly.

```{r auth}
auth <- ig_auth("demo_user", "demo_pass", "demo_api_key", demo = TRUE)
auth
```

# Search markets (mock)

Use `ig_search_markets()` with `mock_response` to simulate the API returning market results.

```{r search}
mock_markets <- data.frame(
  epic = c("TEST.EURUSD", "TEST.GBPUSD"),
  instrumentName = c("EUR/USD", "GBP/USD"),
  stringsAsFactors = FALSE
)

markets <- ig_search_markets("EUR/USD", auth = auth, mock_response = mock_markets)
markets
```

# Current price (mock)

Simulate a current price response.

```{r price}
mock_price <- data.frame(bid = 1.1234, offer = 1.1238, timestamp = Sys.time(), stringsAsFactors = FALSE)
price <- ig_get_price("TEST.EURUSD", auth = auth, mock_response = mock_price)
price
```

# Historical prices (mock)

Simulate historical OHLC data.

```{r historical}
mock_hist <- data.frame(
  snapshotTime = as.character(Sys.Date() - 2:0),
  open = c(1.12, 1.13, 1.11),
  high = c(1.14, 1.15, 1.12),
  low = c(1.11, 1.12, 1.09),
  close = c(1.13, 1.11, 1.10),
  stringsAsFactors = FALSE
)

hist <- ig_get_historical("TEST.EURUSD", from = Sys.Date() - 2, to = Sys.Date(), resolution = "D", auth = auth, mock_response = mock_hist)
hist
```

# Accounts (mock)

Simulate account summary retrieval.

```{r accounts}
mock_accounts <- data.frame(accountId = "ACCT123", balance = 10000, preferred = TRUE, stringsAsFactors = FALSE)
accounts <- ig_get_accounts(auth = auth, mock_response = mock_accounts)
accounts
```

# Logout (mock)

```{r logout}
ig_logout(auth)
Sys.unsetenv("IGFETCHR_TESTING")
```

# Notes

- The vignette uses the built-in testing mode so it runs quickly and without network, satisfying CRAN checks.
- Real API usage requires a free API key from https://labs.ig.com and valid credentials. Replace the mock usage above with real calls and remove the testing environment variable when running live.
